Prefetching SPARQL query cacher

### 2016-05-16 dissertation/cache-proxy.tex
planning

>>>>

When a query is parsed, algebra objects are generated. Based on the
algebra tree, models (which may delegate the task to the store) may
generate plans for any algebra object of their choosing by
implementing the \pmodule{Attean::API::CostPlanner} role. This amounts
to implementing \pcode{plans\_for\_algebra} and
\pcode{cost\_for\_plan} methods. For a given algebra, Attean's query
planner will trust that the model's \pcode{plans\_for\_algebra} is
better than its own by default, a choice that was justified in
\cite{williamspushing}. Additionally, Attean has a simpler mechanism
for single triple or quad patterns: By default, triple or quad
patterns are evaluated by calling the store's \pcode{get\_triples} or
\pcode{get\_quads}, but this may be augmented by adding a wrapper
around an \pcode{access\_plans} method used by the query planner to
produce further plans.

Based on the algebra tree and plans generated by the models or the
default query planner, as well as the access plans, several
alternative plans will be generated, and their cost will be
estimated. How this happens in detail depends on how the planner is
composed. Attean comes with two roles that implement different
planners, \pmodule{Attean::API::SimpleCostPlanner} will compute all
possible plans and then estimate the cost of all plans, and finally
return the best 5. \pmodule{Attean::API::IDPJoinPlanner}, which
implements an Iterative Dynamic Programming planner
\cite{Kossmann:2000:IDP:352958.352982}, which prunes plans
aggressively based on their estimated cost in each iteration of query
plan generation. When a final plan tree has been found, the query may
be executed.
